Virtualisierung eines Echtzeit-Betriebssystems zur Steuerung eines Roboters mit Schwerpunkt auf die Einhaltung der Echtzeit

### 2024-04-02 Masterarbeit_Robotik_Pamuk.tex
bcc, problem_solution, application context

\clearpage
\section{Application Context}
This master's thesis was written at SIGMATEK GmbH \& Co KG \cite{pixelartSIGMATEKKompletteAutomatisierungssysteme}. This section provides necessary information about the starting point and boundary conditions of the thesis, as the work should be reproducible with the means used.

SIGMATEK uses its own customized Linux distribution to be run on their self-manufactured CPUs, namely Salamander 4. This operating system

, to employ hard real-time in their Salamander4 is virtualized through third party services.

The details of this operating system are explained in section \ref{sec:salamander4}

@@

\section{Problem and task definition}
In robotics, accurate and timely control is crucial to ensure precise movements and reliable interaction with the environment. However, existing robot control systems often have limitations in terms of real-time capabilities and communication efficiency, which can have a detrimental effect on response time and reliability. The challenge is to develop a powerful real-time robot control platform that overcomes these limitations and improves the performance of robotic applications.

@@

This integration is expected to lead to a significant improvement in the response time and reliability of robot applications.

@@

In diesem Abschnitt werden sämtliche theoretischen Konzepte und Randbedingungen sowie praktische Methoden, die zur Erreichung der Zielsetzung dieser Masterarbeit beigetragen haben, detailliert beschrieben.

@@

Salamander 4 is the proprietary operating system of SIGMATEK. It is based on Linux version 5.15.94 and integrates Xenomai 3.2, a real-time development environment \cite{XenomaiXenomai}. Salamander 4 is a 64-bit system, which refers to the x86\_64 architecture. The real-time behaviour is achieved through the use of Symmetric Multi-Processing (SMP) and Preemptive Scheduling (PREEMPT). In addition, it utilises IRQPIPE to process interrupts in a way that meets the real-time requirements of the system. The output of the command \texttt{uname -a} can be observed in code \ref{lst:uname_a}.

>>>>

\clearpage
\section{Application Context}
This master's thesis was written at SIGMATEK GmbH \& Co KG \cite{pixelartSIGMATEKKompletteAutomatisierungssysteme}. 
%This section provides necessary information about the starting point and boundary conditions of the thesis, as the work should be reproducible with the means used. 
SIGMATEK uses its own customized Linux distribution to be run on their self-manufactured CPUs, namely Salamander 4. This operating system employs hard real-time with latency requirements between 20 and 50 \textmu s. The goal is to virtualize Salamander 4 and approach the performance of bare metal CPUs. Salamander 4 is virtualized through a third party service, QEMU. The details of this operating system are explained in section \ref{sec:salamander4}.

@@

\section{Problem and task definition}

@@

@@

This section describes in detail all the theoretical concepts and boundary conditions as well as practical methods that contributed to achieving the objectives of this master's thesis.

@@

Salamander 4 is the proprietary operating system of SIGMATEK. It is based on Linux version 5.15.94 and integrates Xenomai 3.2, a real-time development environment \cite{XenomaiXenomai}. Salamander 4 is a 64-bit system, which refers to the x86\_64 architecture. The real-time behaviour is achieved through the use of Symmetric Multi-Processing (SMP) and Preemptive Scheduling (PREEMPT). In addition, it uses IRQPIPE to process interrupts in a way that meets the real-time requirements of the system. The output of the command \texttt{uname -a} can be observed in code \ref{lst:uname_a}.
